Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-01 Submission.Rmd
hyptothesis 1 and figures good to go (Kulas perspective)

H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource. We explore this hypothesis first by item, and then present a more holistic picture. First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability. Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations. Note that the presentation is limited to 8 characteristics per perceived category only because of limited space. All sortable ratings are available in the online resources.

Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only a snapshot - full list available in online resources.

As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`. However, there is considerable disagreement regarding the degree to which job elements are considered hindrances, with the 8 elements showing the *greatest agreement* still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.

Next, we explore the items with the highest variability in perceptions as resources, challenges, and hindrances. Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations. Stated another way, these are the 8 characteristics with the greatest variability in rating. In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as "different".

In addition to highlighting specific items, we also look at the pattern more holistically. Figure \@ref(fig:overallhist) shows that hindrances tend to exhibit similar levels of variability across items. Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram). A Bartlett's test for homogeneity of variance confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

>>>>

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances characteristics that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.

 [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2)  presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).

As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerable less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items. Here, the Figure \@ref(fig:combinegraphs) discrepancies recieve illumination, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are consistently viewed as "different".

### 2023-03-01 Submission.tex
hyptothesis 1 and figures good to go (Kulas perspective)

H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource. We explore this hypothesis first by item, and then present a more holistic picture. First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability. Figure \ref{fig:combinegraphs} presents the top 8 resources, challenges, and hindrances characteristics that are \emph{largely agreed on} as indexed by (relatively) low standard deviations. Note that the presentation is limited to 8 characteristics per perceived category only because of limited space. All sortable ratings are available in the online resources.

Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only a snapshot - full list available in online resources.

As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86. However, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16.

Next, we explore the items with the highest variability in perceptions as resources, challenges, and hindrances. Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations. Stated another way, these are the 8 characteristics with the greatest variability in rating. In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.

In addition to highlighting specific items, we also look at the pattern more holistically. Figure \ref{fig:overallhist} shows that hindrances tend to exhibit similar levels of variability across items. Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram). A Bartlett's test for homogeneity of variance confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).

>>>>

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances characteristics that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.

As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerable less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items. Here, the Figure \ref{fig:combinegraphs} discrepancies recieve illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different''.
